---
title: "Retrieving weather data from free publicly available sources"
#subtitle: "subtitle here"
author: "Johan Ninanya (N0N1)"
date: "`r Sys.Date()`"
#site: bookdown::bookdown_site
#documentclass: book
output:
  rmdformats::readthedown:
    highlight: kate
    number_sections: FALSE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE)
```

- **Johan Ninanya,** International Potato Center (CIP)

# Background {-}

Weather data are important in agriculture and related sciences for activities planning, resources management, crop yield prediction, among others. However, sometimes there are no weather stations on site, so it is necessary to look for some alternatives to supply this need. This notebook aims to explain briefly how weather data can be retrieved from free publicly available sources using R.

**NOTE:** Do not forget that always the best data is the one measured on the site.

# Library loading

For this, the following libraries will be used:
```{r}
library(nasapower)   # nasa database
library(rnoaa)       # noaa database
library(dplyr)       #
library(lubridate)   #

```

# NASA POWER API Client



```{r}
# Specify the location and time period for the data
location <- c(40.7128, -74.0060)  # Latitude and longitude for New York City
start_date <- "2022-01-01"
end_date <- "2022-01-31"

# Specify the variables you want to retrieve (e.g., temperature and solar radiation)
variables <- c("T2M_MAX", "T2M_MIN", "ALLSKY_SFC_SW_DWN")

# Retrieve hourly data
ag_d <- get_power(
  community = "ag",
  lonlat = c(151.81, -27.48),
  pars = c("RH2M", "T2M", "PRECTOTCORR"),
  dates = "2001-01-01",
  temporal_api = "hourly"
)
# View the first few rows of the data
head(ag_d)
```










